{{< var titll >}}

### 2024-10-28 presentation.qmd
mda

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(polynom)
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws1 <- laws_df1 
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
ssr <- selreport(ManifoldDestiny::appsn)
rsr <- selreport(ManifoldDestiny::apprn)
round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
```

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(polynom)
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws1 <- laws_df1 
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
#ssr <- selreport(ManifoldDestiny::apsnn)
#rsr <- selreport(ManifoldDestiny::aprhn)
round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
```
